Supplement to: Learning to Infer Graphics Programs from Hand-Drawn Images

### 2017-07-29 paper.tex
mixture density network description for supplement

  \draw[-{>[scale = 1.5]},very thick,dashed] (next.west) -- ([yshift = -0.2cm]canvas.east) node [midway, below, sloped] (TextNode) {Renderer: \LaTeX~Ti\emph{k}Z};

@@

In the parsing phase, the proposal network currently samples positional variables on a discrete $16\times 16$ grid. More general types of drawings could be supported by instead sampling from continuous distributions, e.g. using Mixture Density Networks~\cite{MDN}.
Implementing a variant of our model that predicts continuous coordinates
using Mixture Density Networks is straightforward;
we have prototyped such a system and
show examples of it working in the supplement.
But, for our collection of hand drawings, discrete positional variables suffice.

>>>>

  \draw[-{>[scale = 1.5]},very thick,dashed] (next.west) -- ([yshift = -0.2cm]canvas.east) node [midway, below, sloped] (TextNode) {Renderer}; %: \LaTeX~Ti\emph{k}Z};

@@

In the parsing phase, the proposal network currently samples positional variables on a discrete $16\times 16$ grid. More general types of drawings could be supported by instead sampling from continuous distributions, e.g. using Mixture Density Networks (MDN)~\cite{MDN}.
Implementing a variant of our model that predicts continuous coordinates
using Mixture Density Networks is straightforward;
we have prototyped such a system and
show examples of it both working and failing in the supplement.
But, for our collection of hand drawings, discrete positional variables suffice,
and currently work much better in practice.
Engineering better handling of the MDN variant of our model is a prime target for future research.

### 2017-07-29 supplement.tex
mixture density network description for supplement

\section{Predicting continuous coordinates using Mixture Density Networks}

@@

Concretely,
we modify our autoregressive drawing command decoder to
predict distributions over real-valued coordinates
as:
\begin{equation}
  p(t_n|t_{1:(n - 1)}) = \text{MDN}_{t_1,n} (a(f|t_{1:(n - 1)}) \oplus \bigoplus_{j < n} t_j)\text{, if }n^{\text{th}}\text{ token is continuous}
\end{equation}
Compare this equation with Equation~\ref{discreteTokenPrediction} to see that we have only
replaced a draw from a multinomial (whose parameters are predicted by an MLP)
with a draw from a mixture of Gaussians (whose parameters are predicted by an MDN).
Otherwise the two models are identical.

@@

\subsection{LSTM Baseline}

>>>>

\subsection{Predicting continuous coordinates using Mixture Density Networks}

@@

Concretely,
we modify our autoregressive drawing command decoder to
predict distributions over real-valued coordinates
as:
\begin{equation}
  p(t_n|t_{1:(n - 1)}) = \text{MDN}_{t_1,n} (a(f|t_{1:(n - 1)}) \oplus \bigoplus_{j < n} t_j)\text{, if }n^{\text{th}}\text{ token is continuous}\label{continuousDensityEquation}
\end{equation}
Compare this equation with Equation~\ref{discreteTokenPrediction} to see that we have only
replaced a draw from a multinomial (whose parameters are predicted by an MLP)
with a draw from a mixture of Gaussians (whose parameters are predicted by an MDN).
Otherwise the two models are identical.

@@

Figure~\ref{syntheticContinuous}  shows the behavior of the MDN variant of our model on noisy synthetic drawings.
Contrast these mediocre results with Figure~4 of the main paper to see that although
our main model is essentially at ceiling for parsing scenes like these,
the MDN variant fares poorly in comparison.
\begin{figure}
  \includegraphics[width = \textwidth]{figures/syntheticContinuous.png}
  \caption{Left column: \LaTeX~output corrupted by noise process designed to resemble the variability is introduced by hand drawings. Right columns: samples from the MDN variant of the model.}\label{syntheticContinuous}
\end{figure}

We evaluated the MDN version of our model on hand drawings by (1)
performing a beam search in order to find the trace maximizing
$\probability [T|I]$, and (2) constraining the predicted coordinates
to lie on the $16\times 16$ grid. We constrain the predicted coordinates
to lie on the grid by integrating the predicted densities about each grid location.
So, using the probability density $p(t_n|t_{1:(n - 1)})$ in Eq.~\ref{continuousDensityEquation},
we compute a probability mass function $\probability [t_n|t_{1:(n - 1)}]$ as:
\begin{equation}
  \probability [t_n = t|t_{1:(n - 1)}] = \int_{t - \frac{1}{2}}^{t + \frac{1}{2}} \mathrm{d}t_n \; p(t_n|t_{1:(n - 1)})\label{constrainingEquation}
\end{equation}
Even after using Eq.~\ref{constrainingEquation} to constrain the predicted coordinates to lie on the $16\times 16$ grid, the MDN variant of the model only produces finished traces for 48/100 of the drawings.
See Figure~\ref{continuousParses} to see the traces recovered by the beam search.

\begin{figure}
  \includegraphics[width = \textwidth]{figures/continuousParses.png}
  \caption{Parsing hand drawings using the MDN variant of our
    model. Black-on-white: hand drawings. White-on-black, below each
    hand drawing: the parse inferred by the model.}\label{continuousParses} 
  \end{figure}
\subsection{LSTM Baseline}
